---
author: 'Ali Kozlu'
date: 'Dec 2018'
institution: 'University Of Pennsylvania'
division: 'Engineering'
advisor: 'Professor Marcus Mitchell'
department: 'Department of Computer and Cognitive Science'
degree: 'Bachelor of Science in Computer and Cognitive Science'
title: 'EAS 499 Final Thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdowndss::thesis_pdf: default
  #thesisdowndss::thesis_gitbook: default
  #thesisdowndss::thesis_word: default
#  thesisdowndss::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content here or
# use code similar to line 20 for the files.  If you are producing in a different
# format than PDF, you can delete or ignore lines 20-31 in this YAML header.
abstract: |
  `r paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`

acknowledgements: |
  
dedication: |
  
preface: |

bibliography: bib/thesis.bib
# Refer to your specific bibliography file in the line above.
csl: csl/apa.csl
# Download your specific csl file and refer to it in the line above.
lot: true
lof: true

space_between_paragraphs: true
# Delete the # at the beginning of the previous line if you'd like
# to have a blank new line between each paragraph
header-includes:
  - \usepackage{amsmath}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---

<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of metadata used to produce the document.  Be careful with spacing in this header!

If you'd prefer to not include a Dedication, for example, simply delete lines 17 and 18 above or add a # before them to comment them out.  If you have other LaTeX packages you would like to include, delete the # before header-includes and list the packages after hyphens on new lines.

If you'd like to include a comment that won't be produced in your resulting file enclose it in a block like this.
-->

<!--
If you receive a duplicate label error after knitting, make sure to delete the index.Rmd file and then knit again.
-->

```{r include_packages, include = FALSE}

# This chunk ensures that the thesisdowndss package is
# installed and loaded. This thesisdowndss package includes
# the template files for the thesis.
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdowndss))
  devtools::install_github("akozlu/thesisdowndss")
library(thesisdowndss)
```
```{r include=FALSE}
library(feather)
library(RcppCNPy)
library(parallel)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(Hmisc)
library(PerformanceAnalytics)
library(shiny)
```
<!-- You'll need to include the order that you'd like Rmd files to appear in the _bookdown.yml file for
PDF files and also delete the # before rmd_files: there.  You'll want to not include 00(two-hyphens)prelim.Rmd
and 00-abstract.Rmd since they are handled in the YAML above differently for the PDF version.
-->

<!-- The {.unnumbered} option here means that the introduction will be "Chapter 0." You can also use {-} for no numbers
on chapters.
-->
Bounce rate defined as: the percentage of visitors to a particular website who navigate away from the site after viewing only one page.
# Introduction {.unnumbered}
This report was commissioned to investigate the results our recent A/B experiment. The goal of the experiment was to test a potential change to the categories displayed on our mobile home page. The suggested adjustment was to display the 10 categories nearest to the user’s location, instead of displaying the 10 most popular categories based on sales. Much of our analysis will use two main metrics, namely conversion and bounce rate, to see how much revenue and click rate is earned in each variation. The goal is to decide whether we should deploy the new webpage (variant) or to revert to the current page (control). Our main dataset consists 6 million users who have visited our mobile home page between Oct 10 2014 and Oct 30 2014. The relevant data gathered for each user profile can be seen in Table \@ref(tab:datasetbreakdown). The report will start by presenting the main findings on our two main metrics. It will then analyze the findings and suggest areas of improvement that can help us make a more informed decision.     the NFL teams spend a significant amount of time each week breaking down film and tagging play in search of opponent tendencies and patterns. In addition, the staff pays attention to what other offenses around the league are doing to compare the revenue and click rate generation of two variations. and  if they can "steal" plays from other teams to add to their playbook. A coach can, for example, look what concepts the other teams are running from a particular formation and adapt a certain version of that play to their playbook. This process is very time intensive, as it requires the staff to go through all the film and label (tagging) play data by hand. It is almost certain that with the NFL’s available player tracking data, this process will soon be automatized through unsupersived machine learning models. However, even if the routes are labeled according to models, a route is only a vector (meaning that it has a specific direction and speed) movement taken by a specific receiver. A better input to the staff is to classify is a pre-packaged pattern of routes, which is usually denoted as a route concept. Thus the aim of the route classifier is to use the information as input to identify a route concept, as done in real life film tagging. Which concepts to classify is dependent to input from the staff, as we can try to classify medium pass level concepts such as levels or mesh concepts. We can also choose to classify higher level concepts such as rub route plays, which can come from different formations and different route combinations. The goal of the present thesis is to see how a singular concept can be classified using trajectory data. Specifically it attempts to use state of the art patiotemporal information systems from fields such as biology and GPS-tracking to classify routes into a stem, pivot (turning point) and branch components and identify a rub route concept, the slant-flat. In doing so, it will explore appropriate means of feature engineering for route evaluation, and specific challenges of classifying route concepts. ^[You can find the Python script used for this project [here.](https://github.com/akozlu/NFLModel)

\clearpage
----------------------------------------------------------------------------------
Column Explanation                              Data Columns     
--------------------------------------------- ------------------
Date of user's visit                                Date
  
How the user arrived at our website                 Channel         
  
New or returning visitor to the website             User Type                 
  
1 if landed directly, 0 if navigated                 Land
from another page on our site             
  
1 if left website after landing,                    Bounce
0 if navigated to another page after landing

1 if purchased, else 0                             Purchase

Number of visitors in control that satisfy    Visitors_Variant
above criterion                                   

Number of visitors in control that satisfy    Visitors_Control
above criterion        

-------------------------
Table: (\#tab:datasetbreakdown)  Breakdown of the dataset used for experiment

